---
title: "Pricing model evaluation"
author: "Arnold Kakaš"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Price prediction model

### Introduction

In this post I will go through <strong> price prediction model </strong> based on dataset [explored]() in my previous post.



### Libraries
```{r message=FALSE, warning=FALSE}
# load libs
pacman::p_load(tidyverse,
               tidymodels)
```


### Final pricing model
Since the goal of this model is to predict price XXXXXXXXXXXXXXXXXXXXXXXXXXX

<br>

The word "Final" in this section may tell you, that there were multiple versions of the model. Indeed, I tried several models - linear regression, random forest and xgboost. 

### Model evaluation

For model evaluation I will use test data dataframe that was used also in modeling process.
```{r}
# load data for model evaluation
apartments_test <- import("data/apartments_test.RDS")
model <- import("data/model.RDS")
```


```{r}
model %>%
  fit(data = apartments_test) %>%
  pull_workflow_fit() %>%
  vip(num_features = 10,
      geom = "point")
```
